---
title: "St. Louis Lead Inequity"
author: "Mariam Garcia"
format: html
---
```{r}

library(tidyverse)
library(janitor)

stl_lead <- read_csv(here::here("data","stl_lead.csv")) %>% 
  clean_names()

#some summary statistics

summary(stl_lead)
head(stl_lead)
tail(stl_lead)
```

```{r}
#making a new data frame from stl_lead

stl_lead_prop <- data.frame(stl_lead) %>% 
  mutate(prop_white= white/total_pop*100)

```

Making a scatterplot graph of the percentage of children in each census tract with elevated blood lead levels vs percent of each census tract identifying as white. 
```{r}
stl_lead_plot<- ggplot(data=stl_lead_prop, aes(x=pct_elevated, y=prop_white)) +
  geom_jitter(aes(size= pct_elevated,color= pct_elevated), alpha= .5)+
  scale_color_gradient(low='red',high='purple')+
    labs(title="Correlation between Blood Lead Elevation in Children and Percent White Population")

ggsave(here::here('figs',"stl_lead_plot.png"), width=6, height = 5)

stl_lead_plot

```
In the scatterplot shown above, the relationship between the percentage of children in each census tract with elevated blood lead levels is negatively correlated to the percentage of a white population in a census tract. This means that the lower the percentage of white population, the likelihood that elevated blood lead levels increases.

```{r}
ggplot(data= stl_lead_prop, aes(x=pct_elevated))+
  geom_histogram(fill='red',color='blue') 
ggsave(here::here('figs','pct_histogram.png'))

```

